### 2016-08-31 ReviewComments/response.tex

\documentclass{vldb}
\usepackage{url}
\newcounter{ctResp}
\newcommand{\response}[1]{
\addtocounter{ctResp}{1}
\textbf{Response \arabic{ctResp}:} #1 \\}

\begin{document}
\title{Response to reviewers' comments for Paper \# 278}
\maketitle

We are deeply grateful to all the reviewers for the generous and insightful
suggestions which help us to improve this work to a better level.
In the following, we provide explicit response to each raised concern and address our corresponding revisions in the new submission.

\section{Response to Reviewer 1}

\textbf{1.1} \emph{The main con that I've spotted is the fact that the algorithm might have been
more nicely framed also within the Spark environment by taking advantage of
the various possibilities offered by it (e.g. caching of RDDs)}

\textbf{Response:} We agree with the reviewer that utilizing advanced Spark features
would benefit our solutions. Indeed, our SPARE algorithm has already taken advantages of the Spark-only features: (1) caching of RDDs and (2) DAG execution engine.

As described in Section 5.3, our SPARE algorithm uses a run-time best-fit strategy to achieve load balance. The best-fit strategy allocates the largest unassigned star to the most empty reducer, which balances the workload for each reducer. Since the strategy needs to know the sizes of all stars, it takes place after the map-phase and before the reduce the phase.
Utilizing Spark's DAG execution engine, we can easily augment traditional map-reduce workflow to the map-planning-reduce workflow. Furthermore, we can utilize the RDD caching feature of Spark to store the map result (i.e., RDDs of stars)
during the planning phase and reuse them in the reduce phase.

In Section 6.2.2 Figure 8, we validate the benefits of adopting these Spark features. In Figure 8, we compare SPARE with
SPARE-RD. SPARE-RD is identical to SPARE except without best-fit strategy. Benefit from the two Spark features, planning
phase only takes around 4\% of SPARE's total execution time. With the planning phase, SPARE is 15\% faster compared to SPARE-RD.

%As described in Section 5.3, our SPARE algorithm uses a run-time best-fit strategy to achieve load balance. Using the DAG execution engine, we are able to augment traditional Map-Reduce workflow to the Map-Planning-Reduce workflow. With the support of in-memory caching of RDDs,
%the Map results need not to be recomputed after the planning phase. As the result shown in Figure 8,  SPARE with best-fit strategy saves 15\% total time as compared to the randomly partition strategy (i.e., SPARE-RD).  If without Spark's features, such an optimization would be hardly possible, but SPARE-RD is still more efficient than the baseline TRPM.

We do not consider utilizing other Spark extensions such as Spark-GraphX, Spark-Streaming and Spark-MLlib because these extensions, as their name suggest, are for different application scenarios.

### 2016-08-31 ReviewComments/review2.tex
Revised response 1

\emph{The GCMP generalization is not particularly novel. Putting a maximum gap size
on consecutive segments is well-known
in sequence mining published more than
10 years ago.}

\response{
We admit that the gap parameter is also used in
mining Gap-restricted Sequential Patterns (GSP). However, the novelty
of this paper is not merely on introducing the gap-constraint to the generalized
co-movement pattern. Instead, we provide a one-stop solution (both in modeling and in technical)
for mining various co-movement patterns with flexible constraints. With
these constraints, users are able to define a more accurate pattern
which are free from the anomalies (e.g., loss-connection anomaly in Figure 2).

Besides, the essence of GSP and GCMP are different. The goal of GSP 
is to find the sequences which conform to the gap constraint and occur frequently.
When counting the occurrence of a sequence in GSP, the object
which a sequence belongs to does not matter. Therefore, 
in a GSP result, the involved objects may be neither
 distinct nor close.
In contrast, GCMP imposes requirements on both the spatial closeness 
of objects and the number of distinct objects.
Due to the unawareness of objects, techniques that are used in GSP 
cannot be directly applied on GCMP. We summarize this difference
in Section 2.5.
%
%When counting the occurrence of a sequence, 
%the object the sequence belongs does not matter. 
%Therefore, a pattern in FS may corresponds to any objects where
%the closeness or distinction of objects are not statisfied. Due
%to this difference, FS solutions cannot be directly applied on GCMP.
%
%
%We agree with the reviewer that gap parameter is 
%also used in the Sequence Mining problem. However, 
%Sequence mining problem is different from the GCMP mining problem. 
%The major difference is that in sequence mining problem, the object
%itself is not considered. In particular, the frequency of a sequence is 
%counted as the occurrence of a sequence. Thus, an object may
%contribute multiple occurrence of a sequence. Conversely, GCMP
%in addition to impose the gap parameter in the temporal constraint, also 
%require the objects in the pattern to be close. Due to this difference,
%Sequence mining solutions cannot support GCMP mining.
%
%that the gap parameter is an old concept. 
%However, the novelty of GCMP lies in the unification and generalization of existing patterns which provide
%a one-stop solution for co-movement pattern detection. And the
%gap parameter merely is used for solving the loose-connection anomaly (as in Figure 2). 
%
%Moreover, the problem of Sequence mining is also different from Trajectory mining.
%The major difference is that sequence mining do not consider the distinction between
%objects and the closeness among objects. This makes the solutions in Sequence mining
%unable to be applied in GCMP. We summarize these points in Section 2.5 of the revised paper.
%
%We agree the fact that the gap parameter is an old concept. Nevertheless, our major contribution in
%modeling lies in unifying existing movement patterns in the trajectory domain. 
%The gap parameter is naturally introduced to 
%solve the loose-connection anomaly (as in Figure 2).
%%which is suffered by the state-of-the-art generalization (i.e., Platoon pattern). 
%In the revision, we add Section 2.5 to accredit the origin of the \emph{gap} concept
%and distinguish the sequential mining problem with our problem. 
}

@@

\emph{Regarding the second weak point, one line of related work is the superimposition
of constraints on spatiotemporal mining. An example is a road network. In other words, given a road network, the network imposes constraints on GCMP.}

>>>>

\textbf{2.1} \emph{The GCMP generalization is not particularly novel. Putting a maximum gap size
on consecutive segments is well-known
in sequence mining published more than
10 years ago.}

\textbf{Response:}
We admit that the gap parameter is also used in
mining Gap-restricted Sequential Patterns (GSP). 
However, the novelty of this paper lies
on the one-stop solution of mining co-movement patterns.
In modeling, we provide the generalize co-movement pattern to
alleviate the troubles
is not merely on introducing the gap-constraint.
Instead, we provide a one-stop solution for mining co-movement patterns. With
our

However, the novelty
of this paper is not merely on introducing the gap-constraint to the generalized
co-movement pattern. 
Instead, we provide a one-stop solution (both in modeling and in technical)
for mining various co-movement patterns with flexible constraints.

This solution not only alleviate the cumbersome for designing each
individual patterns, but also

 With
these constraints, users are able to define a more accurate pattern
which are free from the anomalies (e.g., loss-connection anomaly in Figure 2).

Besides, the essence of GSP and GCMP are different. The goal of GSP 
is to find the sequences which conform to the gap constraint and occur frequently.
When counting the occurrence of a sequence in GSP, the object
which a sequence belongs to does not matter. Therefore, 
in a GSP result, the involved objects may be neither
 distinct nor close.
In contrast, GCMP imposes requirements on both the spatial closeness 
of objects and the number of distinct objects.
Due to the unawareness of objects, techniques that are used in GSP 
cannot be directly applied on GCMP. We summarize this difference
in Section 2.5.

@@

\emph{Regarding the second weak points, one line of related work is the superimposition
of constraints on spatiotemporal mining. An example is a road network. In other words, given a road network, the network imposes constraints on GCMP.}
